---
title: "Bio Pipeline Usage"
author: "Dario Righelli"
date: "`r Sys.Date()`"
output: 
  BiocStyle::html_document:
    toc: true
vignette: >
  %\VignetteEncoding{UTF-8} 
editor_options: 
  chunk_output_type: console
---

<!--
%\VignetteEngine{knitr::rmarkdown}
%\VignetteIndexEntry{Bio Pipeline Usage}
-->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


# Requirements 

For the usage you just need to load the **easyreporting** package, which will 
load the **R6** and **rmarkdown** packages.

```{r}
library("easyreporting")
```

# easyreporting instance creation

For simplicity we setup a project directory path starting from the working 
directory for our report, but you can just enter any path.
The **filenamepath** and the **title** parameters are mandatory, while the 
**author(s)** paramenter is optional.

Once created the **easyreporting** class instance, we can use it in our further
code to make other operations.
It stores some variables for us, in order to not be called again during next 
opreations.
For example the name and the path of the report, the type of report
and the general rmarkdown options of the document.

```{r}
proj.path <- file.path(getwd(), "bioinfo_report")

bioEr <- easyreporting$new(filenamepath=proj.path, title="bioinfo_report",
                        author=c("Dario Righelli"))
```


# Downloading Data

For this vignette we previously downloaded an xlsx table from GEO with accession
number [https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE134118](*GSE134118*).

For importing the xls file, we prepared an ad-hoc function called *importData*
stored in the *importFunctions.R* file.

```{r}
bioEr$mkdCodeChunkComplete(message="geneCounts <- importData(system.file('example_data/GSE134118_Table_S3.xlsx', 
                        package='easyreporting'))", 
                sourceFilesList=system.file("code_example/geneFunctions.R", package="easyreporting"))
```

# Counts exploration 

```{r}
bioEr$mkdCodeChunkComplete(message="EDASeq::plotPCA(as.matrix(geneCounts))")
```

# Differential expression

Let's suppose we stored a function for applying edgeR on our counts in an R file.
We called the file *geneFunctions.R* and the function *applyEdgeRExample*.

It will be easy for us to source the file and to call the function with a single
call of easyreporting package.

```{r}
bioEr$mkdCodeChunkComplete(message="degList <- applyEdgeRExample(counts=geneCounts, samples=colnames(geneCounts), contrast='Pleura - Broth')", 
                    sourceFilesList=system.file("code_example/geneFunctions.R", 
                                                package="easyreporting"))
```



```{r}
bioEr$mkdCodeChunkComplete(message="limma::plotMD(degList$test)")
```




