---
title: "easyreporting standard usage"
author: "Dario Righelli"
date: "`r Sys.Date()`"
output: 
  BiocStyle::html_document:
    toc: true
vignette: >
  %\VignetteEncoding{UTF-8} 
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


# Requirements 

For the usage you just need to load the **easyreporting** package, which will 
load the **R6** and **rmarkdown** packages.

```{r}
library("easyreporting")
```

# easyreporting instance creation

For simplicity we setup a project directory path starting from the working 
directory for our report, but you can just enter any path.
The **filenamepath** and the **title** parameters are mandatory, while the 
**author(s)** paramenter is optional.

Once created the **easyreporting** class instance, we can use it in our further
code to make other operations.
It stores some variables for us, in order to not be called again during next 
opreations.
For example the name and the path of the report, the type of report
and the general rmarkdown options of the document.


```{r}
proj.path <- file.path(getwd(), "project_report")

er <- easyreporting$new(filenamepath=proj.path, title="example_report",
                        author=c("Dario Righelli"))
```

# Code Chunks

*Easyreporting* enables to include rmarkdown titles from first (default) to 
sixth **level**.
The good norm, when writing reports, is always to add a title to a new code 
chunk (CC) followed by a natural language text, which describes the CC.

```{r}
er$mkdTitle(title="First Level Title", level=1)

er$mkdGeneralMsg("A simple paragraph useful to describe my code chunk...")
```

## Manually creating a code chunk

The most mechanical way to create and populate a CC is to manually open the CC,
to insert the code, and then to close it.
Here we show how to insert a variable assignenent inside a CC.

```{r}
rd$mkdCodeChunkSt()
variable <- 1
rd$mkdVariableAssignment("variable", "variable", show=TRUE)
rd$mkdCodeChunkEnd()
```
